---
title: "Project 3 - Traffic Data vs Immigration and Population Change for U.S. Cities"
author: "Daniel Schlomer, Jesse Pye"
date: October 2, 2015"
output: html_document
---

***

```{r}
require("jsonlite")
require("RCurl")
require("extrafont")
require("ggplot2")
require("dplyr")
```

***

This is an html file that documents the steps to reproduce our project . This html file presents a visual story about our data and what we discovered about our data using visualization and workflow techniques.

The first thing we did was locate a source of data. We used our traffic data from our last project. In addition, we found new data - we located census data describing population changes in U.S. urban areas from 2010-2014 due to births, deaths, domestic migration, and international immigration. We had to extract, transform, and load this data into an Oracle database.

***

Now, let's do some workflows and visualize our data!

First, we did an inner join over the two sets of data.
```{r}
source("../03 Visualizations/Plot1.R",echo=TRUE)
```

***

Next, we did an outer join with a different visualization
```{r}
source("../03 Visualizations/Plot2.R",echo=TRUE)
```


***

Finally, we used a left join our data with a different visualization
```{r}
source("../03 Visualizations/Plot3.R",echo=TRUE)
```